Towards Patient-Specific Neural Field Modeling using Micro-Electrode Data

### 2011-05-07 ltx/data_paper/DataPaper.tex

\usepackage{amsmath,amssymb,amsfonts,epsfig} % Typical maths resource packages

%\newif\ifpdf
%\ifx\pdfoutput\undefined
%\pdffalse % we are not running PDFLaTeX
%\else
%\pdfoutput=1 % we are running PDFLaTeX
%\pdftrue
%\fi

% \ifpdf
% \usepackage[pdftex]{graphicx}
% \else
% \usepackage{graphicx}
% \fi
\usepackage{color}
\newcommand{\dean}[1]{\textsf{\emph{\textbf{\textcolor{red}{#1}}}}} 
\newcommand{\parham}[1]{\textsf{\emph{\textbf{\textcolor{blue}{#1}}}}}

@@

\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/KernelBasis.pdf}
\end{center}
\caption{{\bf Connectivity kernel basis functions, $n_{\theta}=25$}, $\sigma^2_{\theta}=3.5$.}
\label{fig:KernelBasis}
\end{figure}
\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/DisturbanceWidthEstimation.pdf}
\end{center}
\caption{{\bf Disturbance support estimation}.}
\label{fig:DisturbanceWidthEstimation}
\end{figure}

@@

\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/ConfedenceIntervel.pdf}
\end{center}
\caption{{\bf Cross-section of connectivity kernel estimates over 100 realisation}. An alternative figure which shows estimates outside confedence interval.}
\label{figConfedenceIntervel}
\end{figure}

>>>>

\usepackage{amsmath,amssymb,amsfonts} % Typical maths resource packages

\newif\ifpdf
\ifx\pdfoutput\undefined
\pdffalse % we are not running PDFLaTeX
\else
\pdfoutput=1 % we are running PDFLaTeX
\pdftrue
\fi

\ifpdf
\usepackage[pdftex]{graphicx}
\else
\usepackage{graphicx}
\fi
\usepackage{color}
\newcommand{\dean}[1]{\textsf{\emph{\textbf{\textcolor{red}{#1}}}}} 
\newcommand{\parham}[1]{\textsf{\emph{\textbf{\textcolor{blue}{#1}}}}}

@@

\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/KernelBasis.pdf}
\end{center}
\caption{{\bf Connectivity kernel basis functions, $n_{\theta}=25$}, $\sigma^2_{\theta}=3.5$.}
\label{fig:KernelBasis}
\end{figure}
\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/KernelBasis1.pdf}
\end{center}
\caption{{\bf Connectivity kernel basis functions, $n_{\theta}=25$}, $\sigma^2_{\theta}=3.5$.}
\label{fig:KernelBasis1}
\end{figure}
\begin{figure}[!ht]
\begin{center}
\includegraphics{./Figures/DisturbanceWidthEstimation.pdf}
\end{center}
\caption{{\bf Disturbance support estimation}.}
\label{fig:DisturbanceWidthEstimation}
\end{figure}

@@
